Correspondence Analysis of Two Mode Networks

### 2025-01-29 Reviews and Response/response-memo.tex

\textbf{Response}: Thanks for this suggestion. I have re-plotted the figures using the suggested column ordering.

\underline{Confusing equations}:

\textbf{Reviewer}: \textit{What confused me about eqs. (23) and (24) is that I don't think the (respective) expressions in parentheses are symmetric matrices, and so I don't see how to take an eigenvector. (Each of the rows, but not the columns, sum to 1.)}

\textbf{Response}: Thanks for this observation. You are correct that I did not adequately explain where the eigenvectors corresponding to the CA (and HH) scores come from. You are right that the equations result in row-stochastic matrices (row sums equal 1.0) that are square but not symmetric. You can still do a spectral decomposition of each of these matrices, but the first (dominant) eigenvalue will be 1.0, and the associated eigenvectors will be filled with constant values. So the relevant eigenvector we seek, which is the first CA dimension, is that associated with the \textit{second} largest eigenvalue (and the second CA dimension is that associated with the third, and so forth). Another way of saying it is that we can perform the usual eigendecomposition of the row-stochastic projection matrices, discard the first trivial eigenvalue and eigenvector and treat the second as the first, the third as the second, etc., and that will be equivalent to the CA solution (the same scores that simple CA of the original rectangular Affiliation matrix would yield). The relevant section of the paper has been rewritten to clarify these issues.

### 2025-01-29 main-R1.tex

Both $\mathbf{P}_{pp}$ and $\mathbf{P}_{gg}$ are square ($P \times |P|$ and $|G| \times |G|$) respectively) degree-normalized projection matrices linking people and groups. For the Southern Women data, they are shown in Figure~\ref{fig:dwproj}. Interestingly, one way to interpret the entries in the degree-weighted projection matrices for people and groups is by giving the \textit{probabilities} that a random walker starting at the row node and, following any sequence of $person-group-person'-group'$ hops, will reach the column person. Thus, higher values indicate an affinity or proximity between the people (and the groups in the corresponding matrix).

>>>>

Both $\mathbf{P}_{pp}$ and $\mathbf{P}_{gg}$ are square ($|P| \times |P|$ and $|G| \times |G|$) respectively) degree-normalized projection matrices linking people and groups. Like their constituent matrices, both $\mathbf{P}_{pp}$ and $\mathbf{P}_{gg}$ are row-stochastic (rows constrained to sum to 1.0), but not symmetric, as can be seen in Figure~\ref{fig:dwproj}. Interestingly, one way to interpret the entries in the degree-weighted projection matrices for people and groups is by giving the \textit{probabilities} that a random walker starting at the row node and, following any sequence of $person-group-person'-group'$ hops, will reach the column person. Thus, higher values indicate an affinity or proximity between the people (and the groups in the corresponding matrix). The reason for the asymmetry is that depending on their pattern of connections to other groups, person $i$ may have more ways of indirectly reaching person $j$ than vice versa (unless $i$ and $j$ are connected to exactly the same groups).
